\documentclass{opensource_cv}

\setname{Martin Jurran}{}
\setaddress{Dresden, Germany}
\setmobile{+49 151 11244244}
\setmail{martin@jurran.org}
\setcitizenship{German}
\setlinkedinaccount{https://www.linkedin.com/in/martin-jurran/} 
\setwebsite{https://martin.jurran.org}
\setgithubaccount{https://github.com/martinjurran} 
\definecolor{VibrantLink}{HTML}{5bbab5}
\definecolor{VibrantCyan}{HTML}{47817d}
\setthemecolor{VibrantCyan}

    
\begin{document}

%Create header
\headerview
\vspace{1ex} % white space
%
\motivationalstatement{
I am a technology enthusiast with solid theoretical \& practical skills in software and web development. Interested in creating solutions for challenging topics in complex business domains, with a requirements engineering and system design focus.
}

%
\section{Work experience}
    %
    \datedexperience{IT Specialist (In-House IT Consultant)}{July 2019 - today}
    \explanation{Linde Engineering}{Dresden, Germany}
    \explanationdetail{
    \smallskip
     \coloredbullet\ %
     Delivered state-of-the-art digital solutions to optimize business processes in alignment with the organization’s Digitalization Roadmap, advising management on technology trends and opportunities.

    \smallskip 
    \coloredbullet\ %
    Successfully managed and executed 10+ IT projects, up to 1,500 hours in scope, ensuring on-time delivery within budget, requirements, and project parameters

     \coloredbullet\ %
     Collected, analyzed, and managed complex business requirements using industry-standard requirements engineering methodologies, translating stakeholder needs into actionable technical specifications and ensuring deliverables matched strategic objectives.

     \smallskip
     \coloredbullet\ %
     Pioneered fully automated CI/CD pipelines in Azure DevOps locally to enhance application deployment, reducing manual efforts by an estimated 90\%, improving release consistency, and accelerating time-to-market.

    \smallskip 
    \coloredbullet\ %
    Designed and developed workflow systems and applications used by approximately 3,000 employees across the EMEA region, driving efficiency and supporting critical business operations.
    
    
    \smallskip 
     }
     \explanationdetailskill{
        \createskill{Tech Stack}{Requirements Engineering \cpshalf Project Management \cpshalf Agile Methodologies \cpshalf Power Platform  \cpshalf Vue.js \cpshalf .NET \cpshalf Azure DevOps}
     }
     %
     \datedexperience{Software Engineering Intern}{May 2018 - June 2018} 
    \explanation{Alaymont Ltd.}{Bray, Ireland} 
    \explanationdetail{ 
    \coloredbullet\ %
    Engineered a software solution that digitized complex forms, improving a core business process, empowering users to own their data, and significantly improving operational efficiency while reducing costs
    \smallskip  
     } 
     \explanationdetailskill{
        \createskill{Tech Stack}{JavaScript \cpshalf Vue.js \cpshalf express.js \cpshalf Sass \cpshalf WebStorm}
     }
     %
     \datedexperience{Computer Science Expert Apprentice}{Aug 2016 - July 2019} 
    \explanation{Linde Engineering}{Dresden, Germany} 
    \explanationdetail{ 
    \coloredbullet\ %
    Introduced an IAM solution that automated permissions provisioning across multiple locations, eliminating repetition, improving response time for up to 50 weekly requests, and ensuring scalable on-boarding processes.
     } 
     \explanationdetailskill{
        \createskill{Tech Stack}{Microsoft PowerShell \cpshalf Vue.js \cpshalf VB6 \cpshalf BaaS \cpshalf SharePoint}
     }
%
\section{Selected Projects}
     %
          \datedexperience{Digital HR Processes Using Power Platform}{Mar 2021 - today}
    \explanationdetail{
        \smallskip 
        \coloredbullet\ %
        Concepted and implemented Power Platform-based solutions for HR processes which received extensive internal acknowledgement for improvement of the employee experience
        
        \smallskip 
        \coloredbullet\ %
        Implemented a Vue.js-based application for the management and reporting of employee absences. Used as the single source of truth for absence information, it is directly improving resource management in project execution
     }
          %
    \datedexperience{Rule-Based System for Plant Equipment Classification and Reporting}{Mar 2021 - today}
    \explanationdetail{
     \smallskip
     \coloredbullet\ %
      Developed a user-configurable system to classify and interpret chemical plant equipment data using a rules engine. Designed a flexible and customizable output module that enabled the creation of Equipment Lists tailored to internal standards or external frameworks like CFIHOS.
     }
     %
     \datedexperience{Pipe Stress Analysis Software}{Mar 2023 - Dec 2023}
    \explanationdetail{
    \smallskip 
    \coloredbullet\ %
    Re-engineered the core elements of a procedural codebase for pipe stress analysis, incorporating modern software design patterns while ensuring strict adherence to ASME industry standards.
     }
     %
     \datedexperience{
Data Transformation for Plant Engineering Tools}{Sep 2023 - Dec 2023}
    \explanationdetail{
     \smallskip
     \coloredbullet\ %
     Reverse-engineered closed-source data formats to decode transformation processes, enabling the creation of 100\% automated and orchestrated data flows between proprietary tools.
     
    \smallskip
     }
\section{Education} 
     \datedexperience{Bachelor of Science, Business Information Systems}{Oct 2024 - today}
    \explanation{Fernuniversität in Hagen}{Remote} 
    \datedexperience{Computer Science Expert, System Integration}{Aug 2016 - July 2019}
    \explanation{Akademie für berufliche Bildung gGmbH}{Dresden, Germany} 
%
\section{Volunteering}
\indent
\explanationdetail{
\smallskip 
\coloredbullet\ %
 \textbf{martin.jurran.org}, Blog about software engineering started in Dec 2023 covering topics such as A11Y, Design Patterns, Refactoring and Data Science.
 }
%
\end{document}
